---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## ipl

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/ipl)](https://CRAN.R-project.org/package=ipl)
<!-- badges: end -->

The goal of ipl is to ...


## Description

The `ipl` R package consists of datasets on all IPL matches played in the years 2008-2020, and provides functions to calculate typical crickets statistics. 



## Installation

You can install the development version of ipl like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which shows you how to solve a common problem:

Load `ipl` R package
```{r load package}
library(ipl)
```

1. Calculate Virat Kohli's batting average in the 2016 season
```{r}
bat_avg("V Kohli", 2016)
```

2. Calculate the maximum runs made by Virat Kohli in a match in the 2016 IPL season
```{r}
bat_max("V Kohli", 2016)
```

3. Calculate the number of centuries and half-centuries made by Virat Kohli in the 2016 IPL season
```{r}
cents_halfcents("V Kohli", 2016)
```

4. Calculate Virat Kohli's strike rate in the 2016 IPL season
```{r}
strike_rate("V Kohli", 2016)
```







