---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## ipl

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/ipl)](https://CRAN.R-project.org/package=ipl)
<!-- badges: end -->

The goal of `ipl` is to provide data and functions related to IPL matches and standard cricket statistics. This package allows users to avail of IPL data and conduct analysis of cricketers
using functions of this package, which return data on the strike rate, batting average, and other
commonly used cricket statistics. 


## Description

The `ipl` R package consists of datasets on all IPL matches played in the years 2008-2020, and provides functions to calculate typical crickets statistics. 



## Installation

You can install the development version of ipl like so:

``` {r}
remotes::install_github("Swaha294/ipl")
```

## Example

This is a basic example which shows you how to solve a common problem:

Load `ipl` R package
```{r load package}
library(ipl)
```

1. Calculate Virat Kohli's batting average in the 2016 season
```{r}
bat_avg("V Kohli", 2016)
```

2. Calculate the maximum runs made by Virat Kohli in a match in the 2016 IPL season
```{r}
bat_max("V Kohli", 2016)
```

3. Calculate the number of centuries and half-centuries made by Virat Kohli in the 2016 IPL season
```{r}
cents_halfcents("V Kohli", 2016)
```

4. Calculate Virat Kohli's strike rate in the 2016 IPL season
```{r}
strike_rate("V Kohli", 2016)
```

5. Calculates the number of times a team chooses to start batting and fielding
```{r}
toss_choice("Delhi Daredevils")
```

6. Find the list of bowlers with bowling average above 40
```{r}
bowler_score(40)
```

7. Calculate Rahul Sharma's overs
```{r}
overs("Rahul Sharma")
```

8. Find Rohit Sharma's total number of sixes
```{r}
sixes("Rohit Sharma")
```

9. Find Suresh Raina's total number of fours
```{r}
fours("Suresh Raina")
```

10. Calculate the number of runs conceded by a given bowler across all IPL 
matches from 2008-2020
```{r}
runs("Rahul Sharma")
```

11. Calculate the number of wickets taken by a given bowler across all IPL 
matches from 2008-2020
```{r}
wickets_taken("Rahul Sharma")
```











