---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## ipl

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/ipl)](https://CRAN.R-project.org/package=ipl)
<!-- badges: end -->

The goal of `ipl` is to provide data and functions related to IPL matches and standard cricket statistics. This package allows users to avail of IPL data and conduct analysis of cricketers
using functions of this package, which return data on the strike rate, batting average, and other
commonly used cricket statistics. 


## Description

The `ipl` R package consists of datasets on all IPL matches played in the years 2008-2020, and provides functions to calculate typical crickets statistics. 



## Installation

You can install the development version of ipl like so:

``` {r}
remotes::install_github("Swaha294/ipl")
```

## Example

This is a basic example which shows you how to solve a common problem:

Load `ipl` R package
```{r load package}
library(ipl)
```

1. Calculate Virat Kohli's batting average in the 2016 season
```{r}
bat_avg("V Kohli", 2016)
```

2. Calculate the maximum runs made by Virat Kohli in a match in the 2016 IPL season
```{r}
bat_max("V Kohli", 2016)
```

3. Calculate the number of centuries and half-centuries made by Virat Kohli in the 2016 IPL season
```{r}
cents_halfcents("V Kohli", 2016)
```

4. Calculate Virat Kohli's strike rate in the 2016 IPL season
```{r}
strike_rate("V Kohli", 2016)
```

5. Calculates the wins, losses, and win percentage for a team based on their starting position (batting or fielding)
```{r}
winloss("Sunrisers Hyderabad", 2017)
```

6. Calculates the number of times a team chooses to start batting and fielding
```{r}
toss_choice("Delhi Daredevils")
```

7. Calculate Rahul Sharma's bowler score
```{r}
bowler_score("Rahul Sharma")
```

8. Calculate Rahul Sharma's overs
```{r}
overs("Rahul Sharma")
```

9. Find a batsman's total number of sixes
```{r}
sixes("Rohit Sharma")
```

10. Find a batsman's total number of fours
```{r}
fours("Suresh Raina")
```



