---
title: "ipl_vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ipl_vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ipl)
library(dplyr)
library(ggplot2)
```


The `ipl` package aims at supplying data and functions for analysis of data on the Indian Premier League (IPL). It includes datasets on individual balls played in IPL games between 2008 and 2020, on the games themselves, and on the top 100 IPL batsmen and the top 100 IPL bowlers across time. Furthermore, the package includes simple functions on analysis of individual batsmen and bowlers, and for combined analysis of IPL matches. 


## Inspiration

Cricket is a globally played sport, which extensively uses statistics for analysis of games and individual players. Moreover, the IPL is a game that brings players from across the globe together, thus providing a unique perspective on how different cricketers play together. However, data providing information on these games and players, or functions which allow for statistical analyses of the same are not widely accessible. Thus, we wanted to create a package that makes this analysis of cricketers easier, since users do not have to worry about data wrangling, missing data, or important cricket statistics, and can, instead, begin their analyses on IPL. 


## Basics of tame data


## Who should use this package?

Anyone interested in cricket, and specifically the Indian Premier League, who wants to use actual data and functions to think critically about the game, conduct analyses, and make inferences should use this package. 

## Datasets Included



































